Basic Model formulation

### 2015-04-14 documentation/model_formulation.Rmd
fix initial offset for ODE (starting at 0 instead 1)

d_rho <- function(rho, parms, z = 4) { 
  with(parms, r* b* rho^( 1 + alpha) * (1 - rho/K) - m * rho - (a * rho^( 1 + q) * L)/(1 + a * h * rho^( 1 + q)) )  
  }

# running the ode-solver
ODEglobal_high <- ode(y = 0.9, func = odesys, times = 1.1^(1:50), parms = parms)

@@

# running the ode-solver
ODEglobal_low <- ode(y = 0.1, func = odesys, times = 1.1^(1:50), parms = parms)

>>>>

d_rho <- function(rho, parms, z = 4) { 
  with(parms, r* b* rho^( 1 + alpha) * (1 - rho/K) - m * rho - (a * rho^( 1 + q) * L)/(1 + a * h * rho^( 1 + q)) )  
  } # instead use function from simfunctions.r?

# running the ode-solver
ODEglobal_high <- ode(y = 0.9, func = odesys, times = 1.1^(0:50)-1, parms = parms)

@@

# running the ode-solver
ODEglobal_low <- ode(y = 0.1, func = odesys, times = 1.1^(0:50)-1, parms = parms)
